Implementation of a lattice Boltzmann method for immiscible two-phase flow simulations using the level set method

### 2015-11-15 Paper/paper.tex
Langsam fertig

A more vivid possible application of the algorithm we presented is shown in figure TODO, which shows the transient movement of an oil drop in a lid driven cavity. %Fig TODO shows two rising and coalescing bubbles in a fluid, produced with our code.

The authors want to thank Ian Mitchell for providing the toolbox for level set methods.

%TODO: add some nice pictures

>>>>

A more vivid possible application of the algorithm we presented is shown in \cref{cavity}, which shows the transient movement of an oil drop in a lid driven cavity. It is a known problem that level set methods tend to suffer from mass losses \cite{Thoemmes}, but ... TODO .trotzdem gut?

The authors want to thank Ian Mitchell for providing the toolbox for level set methods.
\begin{figure}
	\hfill\includegraphics[trim = 0mm 8cm 0mm 8.0cm, clip, width=.95\textwidth, natwidth=595,natheight=842]{cavity.pdf}\hspace*{\fill}
	\caption{The transient flow and deformation of a bubble in a lid driven cavity. The black lines show the interface at different points of time and the arrows display the velocity field.}
	\label{cavity}
\end{figure}
